Individual Differenes

### 2023-08-31 Analysis/e1_test.qmd
ordinal models

Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains. Rhat values were generally within an acceptable range, with values <=1.02 (see appendix for diagnostic plots). We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.

We compared varied and constant performance across two measures, deviation and discrimination. Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band. Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively. Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable. Participants who reliably discriminated between velocity bands tended to have positive slopes with values ~1, while participants who made throws irrespective of the current target band would have slopes ~0.

@@

\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
\end{equation}

```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
#| layout-ncol: 2
#| echo: fenced

@@

The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X). Overall, the varied training group showed a larger deviation relative to the constant training group (β = 135, 95% CI [43, 231]). Deviation also depended on target velocity band, with lower bands showing less deviation. See @tbl-e1-bmm-dist for full model output.

@@

## Appendix
{{< include Appendix/E1_Appendix.qmd >}}

>>>>

Each model was set to run with 4 chains, 5000 iterations per chain, with
the first 2500 of which were discarded as warmup chains. Rhat values
were generally within an acceptable range, with values \<=1.02 (see
appendix for diagnostic plots). We used uninformative priors for the
fixed effects of the model (condition and velocity band), and weakly
informative Student T distributions for for the random effects.

We compared varied and constant performance across two measures,
deviation and discrimination. Deviation was quantified as the absolute
deviation from the nearest boundary of the velocity band, or set to 0 if
the throw velocity fell anywhere inside the target band. Thus, when the
target band was 600-800, throws of 400, 650, and 1100 would result in
deviation values of 200, 0, and 300, respectively. Discrimination was
measured by fitting a linear model to the testing throws of each
subjects, with the lower end of the target velocity band as the
predicted variable, and the x velocity produced by the participants as
the predictor variable. Participants who reliably discriminated between
velocity bands tended to have positive slopes with values \~1, while
participants who made throws irrespective of the current target band
would have slopes \~0.

@@

```{=tex}
\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
\end{equation}
```
```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
#| layout-ncol: 2
#| echo: fenced

@@

The model predicting absolute deviation (dist) showed clear effects of
both training condition and target velocity band (Table X). Overall, the
varied training group showed a larger deviation relative to the constant
training group (β = 135, 95% CI \[43, 231\]). Deviation also depended on
target velocity band, with lower bands showing less deviation. See
@tbl-e1-bmm-dist for full model output.

@@

## Appendix

{{< include Appendix/E1_Appendix.qmd >}}

### 2023-08-31 Misc/indv_diff.qmd
ordinal models

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt2 <-GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

@@

>>>>

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
#mt2 <-GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

testAvg |> select(id,condit,bandInt,vx) |>
  group_by(bandInt) |>
  mutate(across(c(vx), list(c = ~ . - mean(.)))) %>% 
  group_by(id,bandInt) %>% 
  mutate(
    across(
      c(vx_c), 
      list(
        # Between-person center (= person's mean)
        b = ~ mean(.), 
        # Within-person center (= deviation from person's mean)
        w = ~ . - mean(.)
      ),
      .names = "{.col}{.fn}"
    )
  ) %>% 
  ungroup()

testAvg |> select(id,condit,bandInt,vx) |> group_by(condit,bandInt) |> summarise(mean(vx))
```

@@

test |> ggplot(aes(x=vx,y=bandInt)) + geom_jitter(width=0,height=0.3)
